PMV: Comparing the prediction accuracy of ISO 7730:2005 and ASHRAE 55:2023

### 2024-08-15 Manuscript/src/sections/results.tex
feat: code to analyse data from studies with three air speed measurements

\subsection{\ac{db2} overview}\label{subsec:comfort-db-overview}
While the \ac{db2} contains \var{entries_db_all} data points, only \var{entries_db_used} entries met the inclusion criteria listed in the Methodology section.
The distribution of the six input variables used to calculate the PMV indices is visualized in Figure~\ref{fig:dist_input_data}.
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/dist_input_data}
    \caption{Distribution of the input variables used to calculate the \ac{pmv} and \ac{pmv-ce} values.
    The data are shown using boxen plots (letter-value plots).
    They depict the median as the center-line and each successive level outward contains half of the remaining data.}
    \label{fig:dist_input_data}
\end{figure*}
The input data distributions are far from uniformity (equal density) across the Standards' applicability ranges.
We were not able to determine the accuracy of the \ac{pmv} and \ac{pmv-ce} formulations for inputs that were lower than the 2.5th and 97.5th percentiles, since we only had a limited number of data points beyond those values.
For example, only \qty{2.5}{\percent} of the available dataset had a \ac{tdb}~$\leq$ than \var{ta_95_perc_min}, this is a problem since both thermal comfort Standards' applicability limits extend to \qty{10}{\celsius}.
This can be explained by the fact that only a few buildings in the world operate at \ac{tdb} lower than this value.
Mainly because an indoor \ac{tdb} lower than \var{ta_95_perc_min} would be deemed to be unsatisfactory by a great number of occupants~\cite{iso7730}.
This lack of data in the \ac{db2} is particularly relevant for \ac{v}.
The \ac{pmv} and \ac{pmv-ce} only differ when the value of \ac{v}~$\geq$~\qty{0.1}{\m\per\s}, however, the median value in the \ac{db2} was \qty{0.08}{\m\per\s} suggesting that most of the data points were collected in buildings with low air movement.
Consequently, we could not reliably test the accuracy of the \ac{pmv} formulations for values of \ac{v}~$\geq$~\var{v_95_perc_max}.

@@

\subsection{Comparison of PMV accuracy in predicting thermal sensation}\label{subsec:model-accuracy-comparison-in-predicting-thermal-sensation}
The \ac{pmv} was developed with the primary aim of predicting \ac{tsv}, consequently, we are comparing the predicted value from the two models with measured \ac{tsv}.
The two models only differ when \ac{v} exceeds \qty{0.1}{\m\per\s};
hence we also present the results for a subset of the data where \ac{v} is higher than \qty{0.2}{\m\per\s} since above this value the differences in the outputs of the two models are more pronounced.
We set the limit to \qty{0.2}{\m\per\s} and not a higher value since, as previously shown in Figure~\ref{fig:dist_input_data}, we could only reliably test the accuracy of the models up to \ac{v} of \var{v_95_perc_max}.
We did not use \qty{0.1}{\m\per\s} as a threshold because the original difference between the two models was \qty{0.2}{\m\per\s} and it was changed to \qty{0.1}{\m\per\s} only in the \gls{55}.
The effect of air movement is perceptible only when the airspeed is sufficiently high to disrupt the body's thermal plume~\cite{zukowska_impact_2012}.
The threshold in the ASHRAE standard was reduced to \qty{0.1}{\m\per\s} to simplify the usability and achieve one threshold for all the air speeds.
% todo call charts a,b,c,d
\begin{figure*}[htb!]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/bar_stacked_model_accuracy_0}
        \caption{All data}
     \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/bar_stacked_model_accuracy_0.2}
        \caption{Only data with \ac{v}~$\geq$~\qty{0.2}{\m\per\s}}
     \end{subfigure}
    \caption{The calculated \ac{pmv} value is grouped by the \ac{tsv} value reported by the participants. 
    The number of data points in each bin of the two charts is the same and this allows us to compare the accuracy of both models.
    The overall prediction accuracy is shown above the chart while the model accuracy of predicting participants grouped by their \ac{tsv} is overlayed over each bar. 
    A random model, randomly selecting a thermal sensation vote would have an overall accuracy of \qty{14}{\percent}.}
    \label{fig:bar_stacked_model_accuracy}
\end{figure*}
Being \ac{tsv} the value reported by participants (i.e., ground truth), in Figure~\ref{fig:bar_stacked_model_accuracy} we grouped participants' responses by \ac{tsv} and reported the simple accuracy of the different \ac{pmv} formulations over each sub-figure.
Both \ac{pmv} formulations underestimated the conditions at which participants are thermally dissatisfied with their environment.
The overall accuracy of the \ac{pmv} and \ac{pmv-ce} were \qty{33}{\percent} and \qty{34}{\percent}, respectively.
Being the classification problem unbalanced, the simple accuracy is not an optimal metric to rate the model prediction accuracy since a default strategy of guessing the majority class would lead to a high overall model accuracy.
A model that would have always predicted `neutral' would have achieved an overall accuracy of \var{perc_tsv_neutral}, the number of participants who voted \ac{tsv}~=~0.
For both models, the simple accuracy decreases by one point when we only include entries with \ac{v}~$\geq$~\qty{0.2}{\m\per\s}.
We want to remind the reader that the number of data points in each bin is different.

In Table~\ref{tab:f1}, we report the F1-scores for both models, using the whole dataset, only keeping entries with \ac{v}~$\geq$~\qty{0.2}{\m\per\s}, and for those with a $\lvert \textrm{PMV}\lvert \leq 1.5$ and $\lvert \textrm{TSV}\lvert \leq 1.5$.
The F1-macro score, which is free from label imbalance, depicts that the accuracy of both models across all metrics is marginally better than random guessing (i.e., \qty{14}{\percent}) for all data.
For the subset of data with \ac{v}~$\geq$~\qty{0.2}{\m\per\s} the F1-macro scores of the \ac{pmv} and \ac{pmv-ce} models improved and the former outperformed the latter.
This is an unexpected result since the \ac{pmv-ce}, to justify its use, should significantly outperform the \ac{pmv} model when analyzing this subset of data.
Finally, the F1-micro and weighted scores of both models increased by about 0.1 when analyzing the dataset with $\lvert \textrm{PMV}\lvert \leq 1.5$ and $\lvert \textrm{TSV}\lvert \leq 1.5$.
% todo compare how the models compare for PMV < |0.5| not |1.5|
However, the macro score, within this range, remained practically unchanged.
\begin{table}[htb!]
    \centering
    \input{tables/f1.tex}
    \caption{F1-score for the \ac{pmv} and \ac{pmv-ce} models for three datasets.}
    \label{tab:f1}
\end{table}

Grouping the results into discrete categories introduces rounding errors since some participants reported \ac{tsv} on a continuous scale and the \ac{pmv} value is a continuous variable.
To compensate for this we plotted the \ac{pmv} and \ac{pmv-ce} values as a function of \ac{tsv} in Figure~\ref{fig:bubble_models_vs_tsv} and we plotted a \ac{lowess} curve.
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/bubble_models_vs_tsv}
    \caption{The \ac{lowess} curve shows the relationship between the raw \ac{pmv} and \ac{tsv} data.
    Raw data were then binned and a bubble chart (circle area is proportional to the number of votes in that bin) was superimposed over the regression curve to aid the visualization of a large dataset.}
    \label{fig:bubble_models_vs_tsv}
\end{figure*}
The curve, in the Figure, is calculated using the individual data and not the binned data.
We only binned the data to aid the visualization of a large dataset.
If the model is to accurately predict the thermal sensation of people, the regression line should pass through the origin of the cartesian plane and have a slope of 1.
The intercepts for the \ac{pmv} is \qty{-0.23} and for the \ac{pmv-ce} is \qty{-0.25} which means that the model has a bias of less than one-quarter of a thermal sensation interval.
This result is aligned with those presented in Figure~\ref{fig:bar_stacked_model_accuracy} where the \ac{pmv} and \ac{pmv-ce} models can predict people who reported to be neutral \qty{55}{\percent} and \qty{58}{\percent} of the times, respectively.
Both \ac{pmv} formulations always under-predicted the thermal sensation of people who reported to be on the extremes of the \ac{tsv};
the slope of the curve was significantly lower than 1.
We discuss in detail in sub-Section~\ref{subsec:sources-of-error} which factors may be the underlying cause of these errors.

@@

\subsection{Model Bias}\label{subsec:model-bias}
\subsubsection{Model Overall Bias}\label{subsubsec:model-overall-bias}
We calculated the overall bias of the model as previously done by \mycite{Humphreys2002} by subtracting the \ac{pmv} and  \ac{pmv-ce} models prediction from the self-reported \ac{tsv}.
Results are presented in Figure~\ref{fig:hist_discrepancies}.
%  We cannot change into a letter value plot since in that case, it would be hard to highlight the number of responses that are within the range from -.5 to 5.
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/hist_discrepancies}
    \caption{}
    \label{fig:hist_discrepancies}
\end{figure*} 
Overall both the \ac{pmv} and \ac{pmv-ce} models have a median bias lower than half of a thermal sensation interval.
Figure~\ref{fig:hist_discrepancies} contains the summary statistics, and the results highlight that the \ac{pmv-ce} had a higher bias than the \ac{pmv} when using the entire dataset.
We report the median and inter-quantile ranges since data are not normally distributed.
When including only the data with \ac{v}~$\geq$~\qty{0.2}{\m\per\s} the median bias of the \ac{pmv} model reduced to \var{bias_median_pmv_0.2} from \var{bias_median_pmv_0}, meaning that at higher speed the \ac{pmv} model improved.
Surprisingly, we found that the median bias for the \ac{pmv-ce} increased to \var{bias_median_pmv_ce_0.2} from \var{bias_median_pmv_ce_0}.
These, together with those presented in Table~\ref{tab:f1}, are worrying results since the \ac{pmv-ce} model claims to have a higher accuracy at higher values of \ac{v}, but this is not what was found from this data.
The \ac{pmv-ce} has a higher bias while making the code more complex and computationally intensive to run.

@@

\paragraph{Measurement Errors}
All the data contained in the \ac{db2} have been published in peer-reviewed manuscripts, however, measurement errors are inevitably present in the dataset.
This is because all measurement instrumentation is not always calibrated before use, the uncertainty of the measurements may be large, the placement of the instrumentation may not be in the proximity of the participant, and estimating clothing and metabolic rates from tables is a complex and prone to error task.
In an ideal scenario, errors would be random and would cancel out, not significantly affecting the overall bias of the model but only affecting the standard deviation of the error~\cite{Humphreys2002}.
However, this may not always be the case, for example, if a researcher often underestimated the clothing insulation of participants or their activity levels.

>>>>

\subsection{\ac{db2} overview}\label{subsec:comfort-db-overview}
While the \ac{db2} contains \var{entries_db_all} data points, only \var{entries_db_used} entries met the inclusion criteria listed in the Methodology section.
The distribution of the six input variables used to calculate the PMV indices is visualized in Figure~\ref{fig:dist_input_data}.
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/dist_input_data}
    \caption{Distribution of the input variables used to calculate the \ac{pmv} and \ac{pmv-ce} values.
    The data are shown using boxen plots (letter-value plots).
    They depict the median as the center-line and each successive level outward contains half of the remaining data.}
    \label{fig:dist_input_data}
\end{figure*}
The input data distributions are far from uniformity (equal density) across the Standards' applicability ranges.
We were not able to determine the accuracy of the \ac{pmv} and \ac{pmv-ce} formulations for inputs that were lower than the 2.5th and 97.5th percentiles, since we only had a limited number of data points beyond those values.
For example, only \qty{2.5}{\percent} of the available dataset had a \ac{tdb}~$\leq$ than \var{ta_95_perc_min}, this is a problem since both thermal comfort Standards' applicability limits extend to \qty{10}{\celsius}.
This can be explained by the fact that only a few buildings in the world operate at \ac{tdb} lower than this value.
Mainly because an indoor \ac{tdb} lower than \var{ta_95_perc_min} would be deemed to be unsatisfactory by a great number of occupants~\cite{iso7730}.
This lack of data in the \ac{db2} is particularly relevant for \ac{v}.
The \ac{pmv} and \ac{pmv-ce} only differ when the value of \ac{v}~$\geq$~\qty{0.1}{\m\per\s}, however, the median value in the \ac{db2} was \qty{0.08}{\m\per\s} suggesting that most of the data points were collected in buildings with low air movement.
Consequently, we also could not reliably test the accuracy of the \ac{pmv} formulations for values of \ac{v}~$\geq$~\var{v_95_perc_max}.

@@

\subsection{Comparison of PMV accuracy in predicting thermal sensation}\label{subsec:model-accuracy-comparison-in-predicting-thermal-sensation}
The \ac{pmv} was developed with the primary aim of predicting \ac{tsv}, consequently, we are comparing the predicted value from the two models with measured \ac{tsv}.
The two models only differ when \ac{v} exceeds \qty{0.1}{\m\per\s};
hence we also present the results for a subset of the data where \ac{v} is higher than \qty{0.2}{\m\per\s} since above this value the differences in the outputs of the two models are more pronounced.
We set the limit to \qty{0.2}{\m\per\s} and not a higher value since, as previously shown in Figure~\ref{fig:dist_input_data}, we could only reliably test the accuracy of the models up to \ac{v} of \var{v_95_perc_max}.
We did not use \qty{0.1}{\m\per\s} as a threshold because the original difference between the two models was \qty{0.2}{\m\per\s} and it was changed to \qty{0.1}{\m\per\s} only in the \gls{55}.
The effect of air movement is perceptible only when the airspeed is sufficiently high to disrupt the body's thermal plume~\cite{zukowska_impact_2012}.
The threshold in the ASHRAE standard was reduced to \qty{0.1}{\m\per\s} to simplify the usability and achieve one threshold for all the air speeds.
In the supplementary material, we also present the results generated using those entries with \ac{v}~$\geq$~\qty{0.2}{\m\per\s} and from those studies that measured \ac{v} at three different heights.
% todo add results to supplementary material and reference to section in the supplementary material

Being \ac{tsv} the value reported by participants (i.e., ground truth), in Figure~\ref{fig:bar_stacked_model_accuracy} we grouped participants' responses by \ac{tsv} and reported the simple accuracy of the different \ac{pmv} formulations over each sub-figure.
% todo call charts a,b,c,d
\begin{figure*}[htb!]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/bar_stacked_model_accuracy_0}
        \caption{All data}
     \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/bar_stacked_model_accuracy_0.2}
        \caption{Only data with \ac{v}~$\geq$~\qty{0.2}{\m\per\s}}
     \end{subfigure}
    \caption{The calculated \ac{pmv} value is grouped by the \ac{tsv} value reported by the participants.
    The number of data points in each bin of the two charts is the same and this allows us to compare the accuracy of both models.
    The overall prediction accuracy is shown above the chart while the model accuracy of predicting participants grouped by their \ac{tsv} is overlayed over each bar.
    A random model, randomly selecting a thermal sensation vote would have an overall accuracy of \qty{14}{\percent}.}
    \label{fig:bar_stacked_model_accuracy}
\end{figure*}
Both \ac{pmv} formulations underestimated the conditions at which participants are thermally dissatisfied with their environment.
The overall accuracy of the \ac{pmv} and \ac{pmv-ce} were \qty{33}{\percent} and \qty{34}{\percent}, respectively.
Being the classification problem unbalanced, the simple accuracy is not an optimal metric to rate the model prediction accuracy since a default strategy of guessing the majority class would lead to a high overall model accuracy.
A model that would have always predicted `neutral' would have achieved an overall accuracy of \var{perc_tsv_neutral}, the number of participants who voted \ac{tsv}~=~0.
For both models, the simple accuracy decreases by one point when we only include entries with \ac{v}~$\geq$~\qty{0.2}{\m\per\s}.
We want to remind the reader that the number of data points in each bin is different.

In Table~\ref{tab:f1}, we report the F1-scores for both models, using the whole dataset, only keeping entries with \ac{v}~$\geq$~\qty{0.2}{\m\per\s}, and for those with a $\lvert \textrm{PMV}\lvert \leq 1.5$ and $\lvert \textrm{TSV}\lvert \leq 1.5$.
The F1-macro score, which is free from label imbalance, depicts that the accuracy of both models across all metrics is marginally better than random guessing (i.e., \qty{14}{\percent}) for all data.
For the subset of data with \ac{v}~$\geq$~\qty{0.2}{\m\per\s} the F1-macro scores of the \ac{pmv} and \ac{pmv-ce} models improved and the former outperformed the latter.
This is an unexpected result since the \ac{pmv-ce}, to justify its use, should significantly outperform the \ac{pmv} model when analyzing this subset of data.
Finally, the F1-micro and weighted scores of both models increased by about 0.1 when analyzing the dataset with $\lvert \textrm{PMV}\lvert \leq 1.5$ and $\lvert \textrm{TSV}\lvert \leq 1.5$.
% todo compare how the models compare for PMV < |0.5| not |1.5|
% todo check the results
However, the macro score, within this range, remained practically unchanged.
\begin{table}[htb!]
    \centering
    \input{tables/f1.tex}
    \caption{F1-score for the \ac{pmv} and \ac{pmv-ce} models for three datasets.}
    \label{tab:f1}
\end{table}

Grouping the results into discrete categories introduces rounding errors since some participants reported \ac{tsv} on a continuous scale and the \ac{pmv} value is a continuous variable.
To compensate for this we plotted the \ac{pmv} and \ac{pmv-ce} values as a function of \ac{tsv} in Figure~\ref{fig:bubble_models_vs_tsv} and we plotted a \ac{lowess} curve.
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/bubble_models_vs_tsv}
    \caption{The \ac{lowess} curve shows the relationship between the raw \ac{pmv} and \ac{tsv} data.
    Raw data were then binned and a bubble chart (circle area is proportional to the number of votes in that bin) was superimposed over the regression curve to aid the visualization of a large dataset.
    The black dashed line represents the ideal line where the slope is 1 and the intercept is 0.}
    \label{fig:bubble_models_vs_tsv}
\end{figure*}
The curve, in the Figure, is calculated using the individual data and not the binned data.
We only binned the data to aid the visualization of a large dataset.
If the model is to accurately predict the thermal sensation of people, the regression line (black continuous line) should pass through the origin of the cartesian plane and have a slope of 1.
This ideal line is represented by the black dashed line.
The intercepts for the \ac{pmv} is \qty{-0.23} and for the \ac{pmv-ce} is \qty{-0.25} which means that the model has a bias of less than one-quarter of a thermal sensation interval.
This result is aligned with those presented in Figure~\ref{fig:bar_stacked_model_accuracy} where the \ac{pmv} and \ac{pmv-ce} models can predict people who reported to be neutral \qty{55}{\percent} and \qty{58}{\percent} of the times, respectively.
Both \ac{pmv} formulations always under-predicted the thermal sensation of people who reported to be on the extremes of the \ac{tsv};
the slope of the curve was significantly lower than 1.
We discuss in detail in sub-Section~\ref{subsec:sources-of-error} which factors may be the underlying cause of these errors.

@@

\subsection{Model Bias}\label{subsec:model-bias}
\subsubsection{Model Overall Bias}\label{subsubsec:model-overall-bias}
We calculated the overall bias of the model as previously done by \mycite{Humphreys2002} by subtracting the \ac{pmv} and  \ac{pmv-ce} models prediction from the self-reported \ac{tsv}.
Results are presented in Figure~\ref{fig:hist_discrepancies}.
%  We cannot change into a letter value plot since in that case, it would be hard to highlight the number of responses that are within the range from -.5 to 5.
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/hist_discrepancies}
    \caption{}
    \label{fig:hist_discrepancies}
%    todo add caption
\end{figure*} 
Overall both the \ac{pmv} and \ac{pmv-ce} models have a median bias lower than half of a thermal sensation interval.
Figure~\ref{fig:hist_discrepancies} contains the summary statistics, and the results highlight that the \ac{pmv-ce} had a higher bias than the \ac{pmv} when using the entire dataset.
We report the median and inter-quantile ranges since data are not normally distributed.
When including only the data with \ac{v}~$\geq$~\qty{0.2}{\m\per\s} the median bias of the \ac{pmv} model reduced to \var{bias_median_pmv_0.2} from \var{bias_median_pmv_0}, meaning that at higher speed the \ac{pmv} model improved.
Surprisingly, we found that the median bias for the \ac{pmv-ce} increased to \var{bias_median_pmv_ce_0.2} from \var{bias_median_pmv_ce_0}.
These, together with those presented in Table~\ref{tab:f1}, are worrying results since the \ac{pmv-ce} model claims to have a higher accuracy at higher values of \ac{v}, but this is not what was found from this data.
The \ac{pmv-ce} has a higher bias while making the code more complex and computationally intensive to run.

@@

\paragraph{Measurement Errors}
All the data contained in the \ac{db2} have been published in peer-reviewed manuscripts, however, measurement errors are inevitably present in the dataset.
This is because all measurement instrumentation is not always calibrated before use, the uncertainty of the measurements may be large, the placement of the instrumentation may not be in the proximity of the participant, and estimating clothing and metabolic rates from tables is a complex and prone to error task.
In an ideal scenario, errors would be random and would cancel out, not significantly affecting the overall bias of the model but only affecting the standard deviation of the error~\cite{Humphreys2002}.
However, this may not always be the case, for example, if a researcher often underestimated the clothing insulation of participants or their activity levels.
% todo add an additional sentence also about the airspeed error measurement

### 2024-08-15 Manuscript/src/sections/titleAbstract.tex
feat: code to analyse data from studies with three air speed measurements

%        Being relatively simple to calculate and included in both the \gls{7730} and \gls{55} Standards, the \ac{pmv} has seen widespread adoption and has been used by professionals worldwide to design and operate buildings and by researchers to predict thermal sensation.
        The \ac{pmv} model, developed by Fanger, is still currently used in its original form in the \gls{7730} although it has a low prediction accuracy, especially outside thermal neutrality.
        Several other formulations have been proposed to compensate for its limitations, one of which is currently used in the \gls{55}.
        The \gls{7730} and \gls{55} are the most widely used thermal comfort Standards worldwide, and their different \ac{pmv} formulations are a source of confusion for many users who find it difficult to decide which model to use.

@@

        We recommend using the original \ac{pmv} instead of the \ac{pmv-ce} and we suggest reducing the applicability limit of the \ac{pmv} within the range $\mid$\ac{pmv}$\mid \leq 0.5$.
        This recommendation already aligns with the \gls{55} Standard's definition which states that the \ac{pmv} model can be used to determine ``the combinations of indoor thermal environmental factors and personal factors that will produce \textit{satisfactory thermal environmental conditions} for a majority of the occupants within the space''.
        The \ac{pmv} model cannot determine the degree to which people are dissatisfied.
        A value higher or lower than \num{.5} or \num{-.5}, respectively only indicates that people are on the `warm' or `cold' side.
        Finally, our results show that the classic assumption that people who are `slightly warm' or `slightly cool' are thermally comfortable leads to under-counting thermal discomfort in our dataset.
        We, hence, recommend in thermal comfort research the use of the thermal preference scale to determine how people perceive their thermal environment.
    \end{abstract}

>>>>

%        Being relatively simple to calculate and included in both the \gls{7730} and \gls{55} Standards, the \ac{pmv} has seen widespread adoption and has been used by professionals worldwide to design and operate buildings and by researchers to predict thermal sensation.
        The \ac{pmv} model, developed by Fanger, is still currently used in its original form in the \gls{7730} although it has a low prediction accuracy, especially outside thermal neutrality.
        Several other formulations have been proposed to compensate for its limitations, one of which is currently used in the \gls{55}.
        The \gls{7730} and \gls{55} are the most widely used thermal comfort Standards worldwide, and their different \ac{pmv} formulations are a source of confusion for many users who often struggle to determine which model is most appropriate for their needs.

@@

        Based on our results, we recommend using the original \ac{pmv} instead of the \ac{pmv-ce} and we suggest reducing the applicability limit of the \ac{pmv} within the range $\mid$\ac{pmv}$\mid \leq 0.5$.
        This recommendation already aligns with the \gls{55} Standard's definition which states that the \ac{pmv} model can be used to determine ``the combinations of indoor thermal environmental factors and personal factors that will produce \textit{satisfactory thermal environmental conditions} for a majority of the occupants within the space''.
        The \ac{pmv} model cannot determine the degree to which people are dissatisfied.
        A \ac{pmv} value higher than \num{.5} or lower than \num{-.5} only indicates that people's thermal sensation is on the `warm' or `cold' side, respectively.
        Finally, our results show that the classic assumption that people who are `slightly warm' or `slightly cool' are thermally comfortable leads to under-counting thermal discomfort in our dataset.
        We, hence, recommend in thermal comfort research the use of the thermal preference scale to determine how people perceive their thermal environment.
    \end{abstract}
